---
title: "DistanceFinder"
author: "Paul M"
date: "12/3/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Distance Finder Problem


First you will need to create some global variables to dictate the parameters of the problem. For example...
```{r globals}
# How many simulations to run?
NumberOfSims <- 10000

# What is the size of the grid?
a <- 10
b <- 5

set.seed(123)  # set the seed for the random number generator - this makes sure the results are reproducible when we are debugging

# Declare a variable or vector variable to keep track of the sum of the distances across all simulations
Distance <- rep(0,NumberOfSims)  # Here's avector which, for now, we fill it with 0s
```


Now simulate the process of choosing points randomly within the grid.
```{r simulate}
for (i in 1:NumberOfSims){
  # generate z1 (so generate it's x and y coordinates)
  z1 <- cbind(runif(1,0,a),runif(1,0,b))
  # generate z2 (likewise)
  z2 <- cbind(runif(1,0,a),runif(1,0,b))

  # Use Pythagoras' theorem to find the distance between them

  # Add the distance to the variable Distance
}
```

So let's see what happened. We'll calculate the average distance and look at the distribution of the distance across all simulations. Imagine we have all the Distances stored in a vector "Distance", then something like the following will work.
```{r output}
cat("\nOur estimate of the expected distance between the two points is ",mean(Distance))
hist(Distance,breaks=25,col="blue")
```

# Things to address:

1. What happens as the sizwe of the rectangle changes? 
2. Let's imagine we fix the area of the rectangle to be some value, R. Among all suxh rectangles, which is the one that maximizes the expected distance between two randomly chosen points.

